---
title: "FA 4"
author: "Cuerdo, N.H., & Morillo, J.M"
date: "2024-03-02"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 5

A geospatial analysis system has four sensors supplying images. The percentage of images supplied by each sensor and the percentage of images relevant to a query are shown in the following table.



                                      sensor   % img supplied   % relevant img
                                        1             15              50
                                        2             20              60
                                        3             25              80
                                        4             40              85

what is the overall percentage of relevant images?

```{r percentage}
sensor <- c(1,2,3,4)
percent_supplied_img <- c(15, 20, 25, 40)
percent_relevant_img <- c(50, 60, 80, 85)

overall_percent <- sum(percent_supplied_img * percent_relevant_img) / 100
```

### Answer
```{r percentage answer}
overall_percent
```

## Number 6

A fair coin is tossed twice.
Let E, be the event that both tosses have the same outcome, that is,
E, = (HH, TT).
Let E, be the event that the first toss is a head, that is, E2 = (HH, HT).
Let Ez be the event that the second toss is a head, that is, Ez = (TH, HH).
Show that E1, E2, and E3 are pairwise independent but not mutually independent.

```{r coin}
sample_space <- c("HH", "TT", "TH", "TT")

E1 <- c("HH", "TT")
E2 <- c("HH", "HT")
E3 <- c("TH", "HH")

prob_E1 <- length(E1) / length(sample_space)
prob_E2 <- length(E2) / length(sample_space)
prob_E3 <- length(E3) / length(sample_space)

prob_E1E2 <- length(intersect(E1, E2)) / length(sample_space)
prob_E1E3 <- length(intersect(E1, E3)) / length(sample_space)
prob_E2E3 <- length(intersect(E2, E3)) / length(sample_space)

pairwise_independent <- prob_E1E2 == prob_E1 * prob_E2 && prob_E1E3 == prob_E1 * prob_E3 && prob_E2E3 == prob_E2 * prob_E3

prob_joint  <- length(intersect(intersect(E1, E2), E3)) / length(sample_space)

mutually_independent <- prob_joint == prob_E1 * prob_E2 * prob_E3

```

### Result of pairwise independent:
```{r results}
pairwise_independent
```

### Result of mutually independent. 
```{r results 2}
mutually_independent
```

Therefore, from the results, E1, E2, and E3 are pairwise independent but not mutually independent. 
