---
title: "FA2_Morillo"
author: "MORILLO, JADE MARCO S."
date: "2024-02-18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

2. An experiment consists of tossing two fair coins. Use R to simulate this experiment 100 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting one head and one tail in any order.

```{r cars}
set.seed(123)
num_simulations <- 100

outcomes <- replicate(num_simulations, sample(c("H", "T"), 2, replace = TRUE))
counts <- table(apply(outcomes, 2, paste, collapse = ""))
relative_frequencies <- prop.table(counts)

cat("Outcome\t\tRelative Frequency")
cat("HH\t\t", ifelse("HH" %in% names(relative_frequencies), relative_frequencies["HH"], 0))
cat("HT\t\t", ifelse("HT" %in% names(relative_frequencies), relative_frequencies["HT"], 0))
cat("TH\t\t", ifelse("TH" %in% names(relative_frequencies), relative_frequencies["TH"], 0))
cat("TT\t\t", ifelse("TT" %in% names(relative_frequencies), relative_frequencies["TT"], 0))
```

3. An experiment consists of rolling a die. Use R to simulate this experiment 600 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting each of 1, 2, 3, 4, 5, and 6.

```{r pressure, echo=FALSE}
set.seed(123)
num_simulations <- 600

outcomes <- sample(1:6, num_simulations, replace = TRUE)
counts <- table(outcomes)
relative_frequencies <- prop.table(counts)

cat("Outcome\t\tRelative Frequency\n")
for (number in 1:6) {
  cat(number, "\t\t", ifelse(number %in% names(relative_frequencies), relative_frequencies[number], 0), "\n")
}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
