---
title: "FA3_Morillo"
author: "MORILLO, JADE MARCO S."
date: "2024-02-25"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2.

A binary communication channel carries data as one of two sets of signals denoted by 0 and 1. Owing to noise, a transmitted 0 is sometimes received as a 1, and a transmitted 1 is sometimes received as a 0. For a given channel, it can be assumed that a transmitted 0 is correctly received with probability 0.95, and a transmitted 1 is correctly received with probability 0.75. Also, 70% of all messages are transmitted as a 0. If a signal is sent, determine the probability that:

(a) a 1 was received;
(b) a 1 was transmitted given than a 1 was received. 

```{r 2}
T0 <- 0.7
T1 <- 1 - T0
R0_given_T0 <- 0.95
R1_given_T1 <- 0.75

R1 <- R0_given_T0 * T0 + R1_given_T1 * T1

T1_given_R1 <- R1_given_T1 * T1 / R1

cat("Probability that a 1 was received:", R1, "\n")
cat("Probability that a 1 was transmitted given that a 1 was received:", T1_given_R1, "\n")

```

## 7.

There are three employees working at an IT company: Jane, Amy, and Ava, doing 10%, 30%, and 60% of the programming, respectively. 8% of Jane’s work, 5% of Amy’s work, and just 1% of Ava‘s work is in error. What is the overall percentage of error? If a program is found with an error, who is the most likely person to have written it? 

```{r 7}
Jane <- 0.10
Amy <- 0.30
Ava <- 0.60

Err_Jane <- 0.08
Err_Amy <- 0.05
Err_Ava <- 0.01

Err_overall <- Jane * Err_Jane + Amy * Err_Amy + Ava * Err_Ava

cat("Overall percentage of error:", Err_overall * 100, "%\n")

error_df <- data.frame(Employee = c("Jane", "Amy", "Ava"), Error_Percentage = c(Err_Jane, Err_Amy, Err_Ava))

most_likely_person <- error_df[which.max(error_df$Error_Percentage), ]

cat("If a program is found with an error, the most likely person to have written it is:", most_likely_person$Employee, "\n")
```

